### 2019-04-02 papers/journal/encoding.tex
table update with tags of constraints

The following constraint encodes no conditions on activities on nodes,
i.e., all the present molecules on the nodes are active.
\begin{align*}
\texttt{NodeFunOn} =& \bigwedge\limits_{i,m} n_{i,m} = a_{i,m}  
\end{align*}
The following constraint encodes that activity of a molecule $m$ on the node is
defined by a Boolean function $\nodef_m$ of presence of molecules present on that node.
\begin{align*}
\texttt{NodeFunBf} =& \bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
\end{align*}
The following constraint encodes no conditions on activities on edges,
i.e., all the present molecules on the edges are active.
\begin{align*}
 \texttt{EdgeFunOn} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
\end{align*}
The following constraint encodes that activity of a molecule $m$ on the edge is
defined by a Boolean function $\edgef_m$ of presence of molecules present on that edge.
\begin{align*}
 \texttt{EdgeFunBf} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
\end{align*}
%
The following constraint encodes that the activity of the molecules on
edges is defined by inhibition by other molecules based on the pairing
matrix. 
\begin{align*}
\texttt{EdgeFunPairing} =&	\begin{aligned}[t]
\bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \land \bigwedge_{m_l \neq m,l \in \{1,..,3\}} e_{i,j,q,m'} \land p_{m, m_l}] \limplies\\
	(\neg b_{i,j,q,m} \land \bigwedge_{\mathclap{m_l \neq m,l, p_{m, m_l} \in \{1,..,3\}}} \neg b_{i,j,q,m_l})\end{aligned}\\
\end{align*}
%
We denote the particular choice of node and edge function combined by \texttt{ActivityFun}.
\begin{align*}
\texttt{ActivityFun} = \texttt{NodeFun}_m \land \texttt{EdgeFun}_m
\end{align*}
\subsubsection{Constraints for stability condition}
%
We use $m$-reachability to encode the stability condition in VTSs.
%
The following constraint recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps
if either there is a direct edge between $i$ and $j$ with $m$ present on the edge or there is a edge between $i^{\prime \prime}$ and
$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
\begin{align*}
  \texttt{Paths}(r) &= \bigwedge\limits_{i,j,m,p} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
\end{align*}
Now we can encode stability using the reachability variables.
and say if there is an $m$-edge between $i$ and $j$, there is
$m$-reachable path from $j$ to $i$.
\begin{align*}
 \texttt{Loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
\end{align*}
We define \texttt{StabilityC} to collect all the stability related constraints.
% 
\texttt{StabilityC} states that every molecule is moving in a cycle.
\begin{align*}
\texttt{StabilityC} = \texttt{Paths}(r) \land \texttt{Loop}(r) 
\end{align*}
% Boolean variable
% F3 and F2 are used to model these constraints.

@@

In the table~\ref{tab:var-grph}, we present the constraints involved in each version.
%
The column two of the table shows that the constraints V1-V8, R1-R2, and D1-D4 are present
for every variant.
%
The column three of the table lists the constraints that are different among the variants.
%
%
One of the restriction is where the activity of the present molecule is dependent on the presence of the other molecules.
%
For example in version B, D, F activity of the molecules on the node is a boolean function of the presence of other molecules on that node; Anb.
%
Similarly for the case of the edge in version C and D; Aeb.
%
In the case of versions F the activity of the molecules on the edges
is described by pairing matrix; Aep.

>>>>

The following constraint encodes no conditions on activities on nodes,
i.e., all the present molecules on the nodes are active.
\begin{align*}
\texttt{FunOnN} =& \bigwedge\limits_{i,m} n_{i,m} = a_{i,m}  
\end{align*}
The following constraint encodes that activity of a molecule $m$ on the node is
defined by a Boolean function $\nodef_m$ of presence of molecules present on that node.
\begin{align*}
\texttt{FunBfN} =& \bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
\end{align*}
The following constraint encodes no conditions on activities on edges,
i.e., all the present molecules on the edges are active.
\begin{align*}
 \texttt{FunOnE} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
\end{align*}
The following constraint encodes that activity of a molecule $m$ on the edge is
defined by a Boolean function $\edgef_m$ of presence of molecules present on that edge.
\begin{align*}
 \texttt{FunBfE} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
\end{align*}
%
The following constraint encodes that the activity of the molecules on
edges is defined by inhibition by other molecules based on the pairing
matrix. 
\begin{align*}
\texttt{FunPairE} =&	\begin{aligned}[t]
\bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \land \bigwedge_{m_l \neq m,l \in \{1,..,3\}} e_{i,j,q,m'} \land p_{m, m_l}] \limplies\\
	(\neg b_{i,j,q,m} \land \bigwedge_{\mathclap{m_l \neq m,l, p_{m, m_l} \in \{1,..,3\}}} \neg b_{i,j,q,m_l})\end{aligned}\\
\end{align*}
%
We denote the particular choice of node and edge function combined by \texttt{ActivityFun}.
\begin{align*}
\texttt{ActivityFun} = \texttt{NodeFun}_m \land \texttt{EdgeFun}_m
\end{align*}
\subsubsection{Constraints for stability condition}
%
We use $m$-reachability to encode the stability condition in VTSs.
%
The following constraint recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps
if either there is a direct edge between $i$ and $j$ with $m$ present on the edge or there is a edge between $i^{\prime \prime}$ and
$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
\begin{align*}
  \texttt{Paths}(r) &= \bigwedge\limits_{i,j,m,p} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
\end{align*}
Now we can encode stability using the reachability variables.
and say if there is an $m$-edge between $i$ and $j$, there is
$m$-reachable path from $j$ to $i$.
\begin{align*}
 \texttt{Loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
\end{align*}
We define \texttt{StabilityC} to collect all the stability related constraints.
% 
\texttt{StabilityC} states that every molecule is moving in a cycle.
\begin{align*}
\texttt{StabilityC} = \texttt{Paths}(r) \land \texttt{Loop}(r) 
\end{align*}
% Boolean variable
% F3 and F2 are used to model these constraints.

@@

In the table~\ref{tab:var-grph}, we present the constraints involved in each version.
%
The column two of the table shows that the constraints $\texttt{EdgeC}$, $\texttt{ActivityC}$, $\texttt{PairingC}$, $\texttt{FusionC}$, $\texttt{StabilityC}$ and $\texttt{Connected}(k)$ are present for every variant.
%
The last two columns of the table lists the activity constraints that are different among the variants.
%
%
%One of the restriction is where the activity of the present molecule is dependent on the presence of the other molecules.
%
%For example in version B, D, F activity of the molecules on the node is a boolean function of the presence of other molecules on that node; Anb.
%
%Similarly for the case of the edge in version C and D; Aeb.
%
%In the case of versions F the activity of the molecules on the edges
%is described by pairing matrix; Aep.
